Demystifying the Dynamic Slicing and SFL Combination

### 2019-02-14 paper/ijcai/paper.tex
section 3.1 comments addressed

In the following, we illustrate the workflow of the \comb{}
approach for this scenario. First, the combined technique picks
components $c_4$ and $c_3$, which appear at the top of the ranking,
for further analysis. (The cutoff point is user-defined.) Second, the
technique picks a failing test $t_2$ to slice the code.  Let us assume
that the slice obtained for the transaction $t_2$ is $\{c_2, c_5\}$,
\ie, it excludes components $c_4$ and $c_3$. Finally, the spectra and
ranking are updated. The right-side of Figure~\ref{fig:illustration}
shows the modified spectra and ranking after slicing test $t_2$
against $c_4$ and $c_3$. It is worth noting that the technique slices
the code for every failing tests. More precisely, the workflow of the
\comb{} approach consists of four steps: 
\begin{enumerate}
  \itemsep0em
  \item\label{step:spectra} Compute spectra $S$ and ranking $R$ for
  the input test suite;
  \item\label{step:susp-files} Select top $k$ most suspicious classes, according to $R$;
  \item\label{step:compute-slice} Compute slicer for every suspicious
    file, obtained in Step~\ref{step:susp-files}, and every failing test;
    \Rui{union of slices of all points ?}
  \item Adjust the spectra $S$, obtained in Step~\ref{step:spectra}, with
    the slices obtained in Step~\ref{step:compute-slice} and recompute ranking.
\end{enumerate}

Intuitively, slicing enables identification of statements in the spectra
whose values can be set to zero, \ie{}, the components marked with $0$
are irrelevant to determine the test output. Let us now observe the
effect of this spectra modification on the ranking. Analyzing the
Ochiai formula, one observes that, for the components $j$ which are
not part of the slice of a failing test, the combination reduces the
value of $\N{11}$ and increases the value of $\N{01}$ \Rui{lower case N?}. Therefore,
suspiciousness of those components decrease. Similar argument applies
to other fault predictors. In the running example,
Figure~\ref{fig:illustration}, components $c_3$ and $c_4$, which are
not in the slice of $t_2$, have their suspiciousness reduced, enabling
the faulty component $c_2$ to rise from the third to the first
position in the ranking.

@@

\Rui{This is too rought. I would not talk about lithium right away.}
Lithium takes as input a function of interest that can be designed according to the problem to be solved. The function of interest determines if the test case output is interesting or not. In this study, interesting means that the test execution path is equal to the expected one. This information can be deducted from the defects stack traces which show the stack of functions called until the thrown of an exception. The interesting function compares both stack traces (from the test under evaluation and the expected one) until the call where the test fails. For each chunk under evaluation, the test is executed after the chunk being deleted from the source code . Both test ($testStk$) and expected ($expStk$) stack traces are filtered. We only consider stack traces until the line where the main exception is launched. These operations are performed by line 3 and 4 from Algorithm 2. Finally, both messages are compared and if equal the chunk will be deleted from the project, i.e., the chunk is not interesting to reveal the fault of the test.

>>>>

In the following, we illustrate the workflow of the \comb{}
approach for this scenario. First, the combined technique picks
components $c_4$ and $c_3$, which appear at the top of the ranking,
for further analysis. (The cutoff point is user-defined.) Second, the
technique picks a failing test $t_2$ to slice the code.  Let us assume
that the slice obtained for the transaction $t_2$ is $\{c_2, c_5\}$,
\ie, it excludes components $c_4$ and $c_3$. Finally, the spectra and
ranking are updated. The right-side of Figure~\ref{fig:illustration}
shows the modified spectra and ranking after slicing test $t_2$
against $c_4$ and $c_3$. It is worth noting that the technique slices
the code for every failing tests. More precisely, the workflow of the
\comb{} approach consists of four steps: 
\begin{enumerate}
  \itemsep0em
  \item\label{step:spectra} Compute spectra $S$ and ranking $R$ for
  the input test suite;
  \item\label{step:susp-files} Select top $k$ most suspicious classes, according to $R$;
  \item\label{step:compute-slice} Compute slicer for every suspicious
    file, obtained in Step~\ref{step:susp-files}, and every failing test;
  \item\label{step:group} Assemble all the resulting slicers of each failing test; 
  \item Adjust the spectra $S$, obtained in Step~\ref{step:spectra}, with
    the slices of each failing test obtained in Step~\ref{step:group} and recompute ranking.
\end{enumerate}

Intuitively, slicing enables identification of statements in the spectra
whose values can be set to zero, \ie{}, the components marked with $0$
are irrelevant to determine the test output. Let us now observe the
effect of this spectra modification on the ranking. Analyzing the
Ochiai formula, one observes that, for the components $j$ which are
not part of the slice of a failing test, the combination reduces the
value of $\N{11}$ and increases the value of $\N{01}$. Therefore,
suspiciousness of those components decrease. Similar argument applies
to other fault predictors. In the running example,
Figure~\ref{fig:illustration}, components $c_3$ and $c_4$, which are
not in the slice of $t_2$, have their suspiciousness reduced, enabling
the faulty component $c_2$ to rise from the third to the first
position in the ranking.

@@

Lithium takes as input a function of interest that can be designed according to the problem to be solved. The function of interest determines if the test case output is interesting or not. In this study, interesting means that the test execution path is equal to the expected one. This information can be deducted from the defects stack traces which show the stack of functions called until the thrown of an exception. The interesting function compares both stack traces (from the test under evaluation and the expected one) until the call where the test fails. For each chunk under evaluation, the test is executed after the chunk being deleted from the source code . Both test ($testStk$) and expected ($expStk$) stack traces are filtered. We only consider stack traces until the line where the main exception is launched. These operations are performed by line 3 and 4 from Algorithm 2. Finally, both messages are compared and if equal the chunk will be deleted from the project, i.e., the chunk is not interesting to reveal the fault of the test.
